\documentclass[UROP.tex]{subfiles}
\begin{document}

\bigskip
\section{\Large Introduction}
	Unmanned Aircraft Systems (UAS's) can be used for surveillance systems, remote sensing, and other activities which would be potentially dangerous for a human pilot.  However, UAS's have many limitations in their communication capabilities.  In many cases, a mechanically steered antenna will be used to communicate with these systems. The antenna produces a beam that carries pivotal information between the user and the aircraft.  Getting this data can mean the difference between being able to steer your drone away from a dangerous situation and losing control.  However, because a mechanical antenna needs to physically turn in order to point the communication beam in the direction of the aircraft, the beam is slow, imprecise, and subject to mechanical wear. The implications of this are very costly both because of the danger imposed by potential communication failure and because mission critical data might be lost.  We propose to design a system that can steer communications without any moving parts.  We would be building on preexisting phased array technology which allows us to direct a beam electronically. This would largely eliminate the aforementioned issues.  This design allows us to steer a beam more quickly which, in turn, opens up a range of possibilities, including managing multiple UAVs at once and managing UAVs from a mobile mount.\\
	
	This project is under the guidance of Prof. Brian Argrow through our Senior Projects course. Prof. Argrow is interested in using the system for long range surveillance of severe weather, such as tornadoes.  The causes of severe weather and the conditions in which it exists are a popular topic in meteorological research today.  This phased array system would enable another method of data collection that does not endanger the researchers out in the field.  We are very passionate about this project because we believe this project can make a real positive difference in the world and possibly even save lives.\\
	
	In addition to the impact this project could make on the world, we believe this project could be extremely important for us personally because we would get invaluable experience in antenna design, software and control, and embedded systems design. Of our team, 2 people are interested in getting PhDs in fields related to controls and we are all interested pursuing Master's degrees. We hope that this project can facilitate our education for many years to come.\\
\end{document}
